DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/evaluation.tex
figure

\subsection{Multicore Performance}
It may not always be the case that all four cores of the Raspberry Pi 3's Cortex A-53 CPU can be used 
solely for the purpose of operating an autonomous vehicle. Thus, we test how the number of cores 
utilized for real-time operations affects the DeepPicar's overall ability to function as an autonomous 
vehicle platform.

>>>>

\subsection{Effect of the Core Count to Inference Timing}
It may not always be the case that all four cores of the Raspberry Pi 3's Cortex A-53 CPU can be used 
solely for the purpose of operating an autonomous vehicle. Thus, we test how the number of cores 
utilized for real-time operations affects the DeepPicar's overall ability to function as an autonomous 
vehicle platform.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/perf_vs_corecnt}
  \caption{Average control loop execution time vs. \#of CPU cores used
    for inferencing by Tensorflow.}
  \label{fig:perf-vs-corecnt}
\end{figure}

### 2017-10-03 paper/overview.tex
typo
figure

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|}
    \hline
    Item                    & cost (\$) \\
    \hline
    Raspberry Pi 3 Model B  & 35 \\
    New Bright 1:24 scale RC car       & 10 \\
    Playstation Eye camera  &  7 \\
    Pololu DRV8835 motor hat&  8 \\
    External battery pack \& misc.   & 10 \\
    \hline
    Total                   & 70 \\
    \hline
  \end{tabular}
  \caption{DeepPicar's bill of materials (BOM)}
  \label{tbl:carbom}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

Nevertheless, the trained models were still able to achieve reasonable
a degree of accuracy, successfully navigating several different tracks 
we trained. The source code, build instruction, and a collection of
self-driving videos of the DeepPicar can be found at:
\url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}

>>>>

\begin{table}[h]
  \centering
  \begin{tabular}{|c|r|}
    \hline
    Item                    & Cost (\$) \\
    \hline
    Raspberry Pi 3 Model B  & 35 \\
    New Bright 1:24 scale RC car       & 10 \\
    Playstation Eye camera  &  7 \\
    Pololu DRV8835 motor hat&  8 \\
    External battery pack \& misc.   & 10 \\
    \hline
    Total                   & 70 \\
    \hline
  \end{tabular}
  \caption{DeepPicar's bill of materials (BOM)}
  \label{tbl:carbom}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

Nevertheless, the trained models were still able to achieve a reasonable
degree of accuracy, successfully navigating several different tracks 
we trained. The source code, build instruction, and a collection of
self-driving videos of the DeepPicar can be found at:
\url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}
